---
title: "Week 11 chapter 8"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gapminder)
library(tidyverse)
library(ggrepel)
library(socviz)
```

## Hands-on 1

Considering American Sociological Association Section Membership dataset (asasec), For 2013 show the relatioship between members and revenues and also cosider different colors for having journal. Use the linear prediction line.


```{r 1, warning = FALSE, message = FALSE}

```

## Hands-on 2

Lebel those outliers with revenue bigger than $10,000

```{r 2, warning = FALSE, message = FALSE}

```

## Hands-on 3

Revise the code below to use *Accent* for color

```{r 3, warning = FALSE, message = FALSE}
p <- ggplot(data = organdata,
            mapping = aes(x = roads, y = donors, color = world))
p + geom_point(size = 1.5) +
    theme(legend.position = "top")
```

## Hands-on 4

Find Lehigh and Rutgers University color codes and dispaly it here 

```{r 4, warning = FALSE, message = FALSE}


```