---
title: "Quiz1"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(gapminder)
library(tidyverse)
library(socviz)
```

## Hands-on 1
Question: By using *vjust* argument in geom_text() function, label all points in the vertical direction above or below each point. (two plots should be drawn, below and above each point by changing the value of *vjust*)

```{r 1, warning = FALSE, message = FALSE}
p <- ggplot(data = by_country,
            mapping = aes(x = roads_mean, y = donors_mean))

p + geom_point() + geom_text(mapping = aes(label = country), vjust = -.2)

```


## Hands-on 2
For the summarized *gss_sm* dataset grouped by only *padeg*, laebl the mean of children and siblings based on the paternal degree.


```{r 2, warning = FALSE, message = FALSE}
library(ggrepel)
by_padeg <- gss_sm %>% group_by(padeg) %>%
  summarize(childs_mean= mean(childs, na.rm = TRUE),
            sibs_mean = mean(sibs, na.rm = TRUE))

p <- ggplot(data = by_bigregion,
            mapping = aes(x = childs_mean, y = sibs_mean))
p + geom_point() + geom_text(mapping = aes(label = padeg), vjust = 1)

# Using geom_text_repel
p_title <- "Father's Highest Degree and the number of Sibling and Children"
p_subtitle <- "General Social Survey 2016 "
p_caption <- "Data from socviz."
x_label <- "Average of Children"
y_label <- "Average of Siblings"

p + geom_point() + geom_text_repel(mapping = aes(label = padeg))+ labs(x = x_label, y = y_label, title = p_title, subtitle = p_subtitle,
         caption = p_caption)



```

## Hands-on 3
Question: For the by-country dataframe, choose observations from the united state of america (ccdoe=USA) after 1998, and then highlight them in the plot of road fatalities average against the average percentage of donors 

```{r 3, warning = FALSE, message = FALSE}
organdata$ind <- organdata$ccode %in% c("USA") &
                    organdata$year > 1998
p <- ggplot(data = organdata,
            mapping = aes(x = roads,
                          y = donors, color = ind))
p + geom_point() +
    geom_text_repel(data = subset(organdata, ind),
                    mapping = aes(label = ccode)) +
    guides(color = "none")   # Remove some guides
```


## Hands-on 4
Using gapminder dataset, specify the outliers in the plot of gdpPercap over lifeExp. 


```{r 4, warning = FALSE, message = FALSE}
library(gapminder)
p <- ggplot(data = gapminder,
            mapping = aes(x = gdpPercap, y = lifeExp)) +
annotate(geom = "rect", xmin = 75000, xmax = 120000,
             ymin = 50, ymax = 70, fill = "red", alpha = 0.2) + 
    annotate(geom = "text", x = 75000, y = 75,
             label = "A surprisingly high gdpPercap \n and average lifeExp.", hjust = 0) 
p + geom_point()
```

